%!TEX root = ../dissertation.tex
\addtocontents{toc}{\protect\thispagestyle{empty}}
\pagenumbering{arabic}
\setcounter{page}{1}
\input{frontmatter/personalize}

\newpage
\thispagestyle{empty}
\vspace{120pt}
\noindent \\
\noindent \\
\noindent \Huge \textbf{\thetitle} \\
\noindent \\
\noindent \\
\noindent \\
\noindent \Large \theauthor\\
\newpage
\rm

\newpage
\thispagestyle{empty}
\vspace*{\fill}
\noindent \small The research presented in this thesis was performed at the Department of Tumor Immunology at the Radboud Institute for Molecular Life Sciences, Radboud University Medical Center, Nijmegen, The Netherlands. The research presented in this thesis was financially supported by an NWO Vidi grant. \\
\noindent \\
\noindent \textbf{ISBN} \\
\noindent 1234567890123 \\
\noindent \\
\noindent \textbf{Design} \\
\noindent P.T.A. Linders \\
\noindent \\
\noindent \textbf{Print} \\
\noindent Gildeprint \\
\noindent \\
\noindent \\
\scshape \noindent \small \textbf{\copyright \small 2021\hspace{3pt}-- \theauthor} \\
\noindent All rights reserved. No part of this book may be reproduced, distributed, stored in a retrieval system or transmitted in any form or by any means, without prior written permission by the author. \\
% \vspace*{\fill}
\newpage
\rm

\thispagestyle{empty}
\vspace*{\fill}
\vspace{10pt}
\begin{center}
    \Huge \textcolor{SchoolColor}{\thetitle} \normalsize \\
    \vspace{100pt}
    \large \textbf{Proefschrift} \normalsize \\
    \vspace{50pt}
    \textsc{ter verkrijging van de graad van doctor\\
        aan de Radboud Universiteit Nijmegen\\
        op gezag van de rector magnificus prof. dr. J.H.J.M. van Krieken,\\
        volgens besluit van het college van decanen\\
        in het openbaar te verdedigen op vrijdag 24 december 2021\\
        om 12.30 uur precies\\
        \vspace{20pt}
        door\\
        \vspace{20pt}}
    \large \textbf{\theauthor} \normalsize \\
    \vspace{12pt}
    geboren op 28 april 1993\\
    te Oss
\end{center} \vspace*{\fill}

\newpage
\thispagestyle{empty}
\vspace{120pt}
\noindent \textbf{Promotoren}\\
\noindent Prof. dr. Geert van den Bogaart (Rijksuniversiteit Groningen)\\
\noindent Prof. dr. Dirk J. Lefeber\\
\noindent \\
\noindent \textbf{Copromotor}\\
\noindent Dr. Martin ter Beest\\
\noindent \\
\noindent \textbf{Manuscriptcommissie}\\
\noindent Harry van den Boekel\\
\newpage
\rm

% \newpage
% \pdfbookmark{\contentsname}{Contents}
% \tableofcontents
% \thispagestyle{empty}
% \rm
% \cleardoublepage